Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
minor edit to difference between neural field and neural mass models

The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability to infer physiological parameters from electrophysiological data. The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies. Large-scale neuroinformatic efforts, such as the Virtual Brain project (www.thevirtualbrain.org \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling. This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation. Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error. Therefore, there exists enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model. Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony. \parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location. } It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.

>>>>

The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability to infer physiological parameters from electrophysiological data. The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies. Large-scale neuroinformatic efforts, such as the Virtual Brain project (www.thevirtualbrain.org \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling. This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation. Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error. Therefore, there exists enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model. Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony. \parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
